Deuteron Electro-Disintegration at Very High Missing Momenta

### 2020-03-23 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/body.tex
updated

by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively. The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as 
$\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$ and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the 3-momentum transfer and $(T_{p}$ and $T_{\mathrm{r}})$ are the
final proton and recoil system kinetic energies, respectively, where the recoil system is assumed to be a neutron. The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).\\

@@

@@

normalization \footnote{Conservative estimates on the systematic uncertainties of the total live and charge were made.
Determination of systematics on these quantities is a work in progress.} and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual

@@

\indent The experimental and theoretical reduced cross sections were extracted and are defined as follows:
\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{Kf_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},

@@

\newpage

@@

\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$, $K$ is a kinematical factor\footnote{The kinematical factor in Eq.\ref{eq:1} is defined as $K\equiv E_{\mathrm{f}}p_{\mathrm{f}}$, where $E_{\mathrm{f}}$ and $p_{\mathrm{f}}$ are the final proton energy and momentum, respectively.},
$f_{\mathrm{rec}}$ is a recoil factor\footnote{The recoil factor in Eq.\ref{eq:1} is obtained by integrating over the deuteron binding energy in the 6-fold differential cross section and is defined as $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$, where
          $E_{\mathrm{f}}$ and $p_{\mathrm{f}}$ are the final proton energy and momentum, respectively.} and $\sigma_{\mathrm{cc1}}$ is the

>>>>

by the new SHMS and the existing High Momentum Spectrometer (HMS), respectively. The beam currents delivered by the accelerator ranged between 45-60 $\mu$A and the beam was rastered over a 2x2 mm$^{2}$ area to reduce the effects of localized boiling on the cryogenic targets (hydrogen and deuterium).\\

@@

\indent The recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$
and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$ where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\

@@

normalization and kinematic uncertainties in the beam energy and spectrometer angle/momentum settings. The individual

@@

\indent The experimental and theoretical reduced cross 

@@

@@

\noindent sections were extracted and are defined as follows:
\sigma_{\mathrm{red}} \equiv \frac{\sigma_{\mathrm{exp(th)}}}{E_{\mathrm{f}}p_{\mathrm{f}}f_{\mathrm{rec}}\sigma_{\mathrm{cc1}}},
\noindent where $\sigma_{\mathrm{exp(th)}}$ is the 5-fold experimental (or theoretical) differential cross section $\frac{d^{5}\sigma}{d\omega d\Omega_{e} d\Omega_{p}}$,
$E_{\mathrm{f}}$ is the final proton energy, $f_{\mathrm{rec}}\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$
is a recoil factor obtained by integrating over the deuteron binding energy in the 6-fold differential cross section, and $\sigma_{\mathrm{cc1}}$ is the

### 2020-03-23 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/introduction.tex
updated

nucleons begin to 
This short distance region is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.

@@

\indent The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
electro-disintegration reaction at $p_{r}>300$ MeV/c neutron recoil (or ``missing'') momenta. Within the PWIA, the virtual photon couples to
the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron). The neutron carries a momentum equal in magnitude but opposite in direction
to the initial state proton, $\vec{p}_{\mathrm{r}} = -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution. \\

@@

electro-production threshold.\\
\indent Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)(See Section 5 of Ref. \cite{sargsian_2015}) have helped quantify the contributions

>>>>

nucleons begin to overlap. This short distance region is directly related to two-nucleon short range correlations (SRC) observed in $A>2$ nuclei \cite{PhysRevC.68.014313,PhysRevLett.96.082501,PhysRevLett.99.072501,Fomin_2017,Barack_2019,RevModPhys.89.045002}.

@@

\indent  Within the PWIA, the virtual photon couples to
the bound proton which is subsequently ejected from the nucleus without further interaction with the recoiling system (neutron). The neutron carries a recoil momentum, $p_{r}$, equal in magnitude but opposite in direction
to the initial state proton, $\vec{p}_{\mathrm{r}} \sim -\vec{p}_{\mathrm{i},p}$, thus providing information on the momentum of the bound nucleon and its momentum distribution.
The most direct way to study the short range structure of the deuteron wave function (or equivalently, its high momentum components) is via the exclusive deuteron
electro-disintegration reaction at $p_{r}>300$ MeV/c.\\

@@

electro-production threshold. Previous deuteron electro-disintegration experiments performed at lower $Q^{2}$ ($Q^{2}<1$ (GeV/c)$^{2}$)(See Section 5 of Ref. \cite{sargsian_2015}) have helped quantify the contributions

### 2020-03-23 MY_PUBLICATIONS/PRL/draft_v4_HCsuggestions/prl.tex
updated

\begin{abstract}
$^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $-Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.01 GeV/c. The data have been obtained at fixed neutron recoil angles
$\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
transfer $\vec q$. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
meson exchange currents (MEC) and isobar configurations (IC) are expected to 
be suppressed and the plane wave impulse approximation (PWIA) provides the
dominant cross section contribution. The new data are compared to recent
theoretical calculations, where a significant disagreement for
missing momenta $p_{r}>700$ MeV/c has been observed. 
\end{abstract}

>>>>

\begin{abstract}
$^{2}\mathrm{H}(e,e'p)n$ cross sections have been measured at 4-momentum transfers of $-Q^{2} = 4.5 \pm 0.5$ (GeV/c)$^{2}$
reaching neutron recoil (missing) momenta up $p_{\mathrm{r}}\sim$ 1.0 GeV/c. The data have been obtained at fixed neutron recoil angles
$\theta_{nq} = 35^\circ$, $45^\circ$ and $75^{\circ}$  with respect to the 3-momentum
transfer $\vec q$. The new data agrees well with previous data which reached $p_{r}\sim500$ MeV/c. At $\theta_{nq} = 35^\circ$ and $45^\circ$, final state interactions (FSI),
meson exchange currents (MEC) and isobar configurations (IC) are
suppressed and the plane wave impulse approximation (PWIA) provides the
dominant cross section contribution. The new data are compared to recent
theoretical calculations, where a significant disagreement for
missing momenta $p_{r}>700$ MeV/c has been observed. 
\end{abstract}
